---
title: "CFLIM"
author: "Martin Monkman"
date: '2022-08-18'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

library(cansim)
```




## Person-count

https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1110001801

After-tax low income status of tax filers and dependants based on Census Family Low Income Measure (CFLIM-AT), by family type and family type composition

Frequency: Annual

Table: 11-10-0018-01 (formerly CANSIM 111-0046)

Release date: 2022-08-09

Geography: Province or territory, Census metropolitan area, Census agglomeration, Census metropolitan area part, Census agglomeration part


## Family count

https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1110002001


After-tax low income status of census families based on Census Family Low Income Measure (CFLIM-AT), by family type and family composition

Frequency: Annual

Table: 11-10-0020-01 (formerly CANSIM 111-0047)

Release date: 2022-08-09

Geography: Province or territory, Census metropolitan area, Census agglomeration, Census metropolitan area part, Census agglomeration part



```{r}

df_cflim <- get_cansim("1110002001")

df_cflim <- df_cflim %>% 
  janitor::clean_names() 

#write_rds(df_cflim, here::here("data_output", "df_cflim.rds"))
#write_csv(df_cflim, here::here("data_output", "df_cflim.csv"))

```

```{r}

ls(df_cflim)

```

```{r}
df_cflim %>% 
  distinct(census_family_type)

df_cflim %>% 
  distinct(family_type_composition)

```



```{r df_victoria}
df_cflim_victoria <- df_cflim %>% 
  filter(uom == "Number",
         census_family_type == "All census families in low income",
         geo == "Victoria, British Columbia") %>% 
  filter(family_type_composition != "Family types with or without children")

df_cflim_victoria

```


```{r ch_victoria}

ggplot(df_cflim_victoria, aes(x = date, y = val_norm, colour = family_type_composition)) +
  geom_line()
```


